Do More Subdivisions in Wards Increase Turnout? An Analysis of the 2022 Toronto Municipal Election

### 2023-06-03 outputs/paper/paper.qmd
Edits to the code to display graphs

# summarize ward data by number of subdivisions

head (summarized_voter_statistics, 60) |>
   kable(
    col.names = c("Ward", "Sub"),
  booktabs = TRUE
  )

>>>>

```{r}
#| message: false
#| echo: false
#| #| label: fig-voter_statistics
#| tbl-cap: Number of Subdivisions per Ward

# summarize ward data by number of subdivisions
summarized_voter_statistics |>
   kable(
    col.names = c("Ward", "Number of Subdivisions"),
  booktabs = TRUE
  )
